Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019

### 2022-12-07 products/paper/main.qmd
Add abstract

---
title: Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019
author: 
  - Aaron Gullickson, *University of Oregon*
abstract: test abstract
thanks: The corresponding author can be reached at aarong@uoregon.edu. Supplementary materials provided with this article include full model results upon which figures are based as well as any senstivity analysis described herein. All code and data for this project are available at ...
format:
  pdf:
    documentclass: scrartcl
    papersize: letter
    fig-height: 4
    fig-pos: t
    keep-tex: false
  docx:
    toc: false
bibliography: ../project.bib
execute: 
  eval: true
  echo: false
  warning: false
  error: false
prefer-html: true
editor: source
csl: american-sociological-association.csl
---

>>>>

---
title: Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019
author: 
  - Aaron Gullickson, *University of Oregon*
abstract: Understanding how outcomes for biracial individuals compare to their monoracial peers is critical for understanding how patterns of racial inequality in the contemporary United States might be shifting. Yet, we know very little about the life chances of biracial individuals due to limitations in most available data sources. In this article, I utilize American Community Survey data from 2010-2019 to examine the risk of being clearly behind expected grade among biracial and monoracial K-12 students, helping to fill a gap in our understanding. With large sample sizes for most biracial groups, I am able to estimate grade retention risk for biracial students with enough precision to differentiate even modest differences in risk relative to monoracial groups. The results indicate that for most biracial groups, biracial students have risk similar to their monoracial constituent group with lower risk. Although biracial students tend to have favorable family resource characteristics, controlling for these characteristics does little to change the overall placement of their outcomes.
thanks: The corresponding author can be reached at aarong@uoregon.edu. Supplementary materials provided with this article include full model results upon which figures are based as well as any senstivity analysis described herein. All code and data for this project are available at ...
format:
  pdf:
    documentclass: scrartcl
    papersize: letter
    fig-height: 4
    fig-pos: t
    keep-tex: false
  docx:
    toc: false
bibliography: ../project.bib
execute: 
  eval: true
  echo: false
  warning: false
  error: false
prefer-html: true
editor: source
csl: american-sociological-association.csl
---
